---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# BioDataome

[BioDataome](http://dataome.mensxmachina.org/) is a collection of uniformly preprocessed and automatically annotated datasets for data-driven biology. The processed data can be accessed via the [BioDataome](http://dataome.mensxmachina.org/) website in .csv format and the BioDataome package via github. BioDataome package contains all the functions used to download, preprocess and annotate gene expression and methylation microarray data from Gene Expression Omnibus, as well as RNASeq data from [recount](https://jhubiostatistics.shinyapps.io/recount/).

## Installation

You can install BioDataome from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mensxmachina/BioDataome")
```

## Useful files

Read BioDataome tutorias:
[BioDataome vignette](http://dataome.mensxmachina.org/documentation)
[BioDataome package help files](BioDataome.pdf)

